\section{Troubleshooting}
\label{sec:troubleshooting}

\QnA[ol-foaming]{The draft beer is foaming}{
    \item Make sure the gas is turned on enough.
    \item If the system is not cold enough (for example, if it was not
    connected before the bar started), you can try to give it a
    break of about an hour so that it can cool down.
    \item It could be a bad keg. Try replacing it with a
    different one.
}

\QnA[low-pressure]{There's hardly any draft beer coming out of the tap}{
    \item Check that the keg is not empty. If it is, put a new one on.
    \begin{itemize}
        \item Lift the handle up.
        \item Turn counterclockwise.
        \item Put the handle on a new keg.
        \item Turn clockwise and make sure it is not crooked.
        \item Press the handle down.
    \end{itemize}
    \item Check that the coupling/handle is properly seated on the keg.
    \item Check that the \textit{quickconnect}\index{Quickconnect} is connected correctly.
    \item Check that the gas is turned on.
    \item Check that the gas is not empty. There are some pressure gauges under
    the bar. There is more gas in the parking garage. Since it is rare
    to change gas, it would be helpful to point out that
    more needs to be purchased: Please send an email to
    \beermail.
}

\QnA[accident]{There has been an accident/power outage/\ldots/the world is ending}{
    \item There is a notice hanging by the bar that describes who
    (operations/police/fire department etc.) to contact in different
    situations, and how they can be contacted.
    \item In the event of an evacuation, the responsible
    bartender should know the emergency exits. There is a map with these (in several
    places) in the Nygaard basement.
}

If you are in a situation that is not mentioned here, you are very welcome to send an email to \webmail,
or make a pull request on \href{https://github.com/fredagscafeen/guides}{GitHub}
with the situation you need described. This will help the guide improve.
